Identifying Extracellular Vesicles of Placenta and Uterine Origin Using RNA Expression Signatures

### 2015-10-12 slides/slides.Rnw
add better slides for ISRS presentation; fix date

\documentclass[ignorenonframetext]{beamer}
\usepackage{fontspec}
\setmainfont{FreeSerif}
\setsansfont{FreeSans}
\setmonofont{FreeMono}
\usepackage{url}
\usepackage{fancyhdr}
\usepackage{graphicx}
\usepackage[bf]{caption}
\usepackage{rotating}
\usepackage{wrapfig}
\usepackage{fancybox}
\usepackage{booktabs}
% \usepackage{multirow}
\usepackage{acronym}
\usepackage{qrcode}
\usepackage[backend=biber,natbib=true,hyperref=true,style=nature]{biblatex}
\addbibresource{references.bib}
% \usepackage[nomargin,inline,draft]{fixme}
% \newcommand{\DLA}[1]{\textcolor{red}{\fxnote{DLA: #1}}}
% \usepackage[hyperfigures,bookmarks,colorlinks,citecolor=black,filecolor=black,linkcolor=black,urlcolor=black]{hyperref}
\usepackage{texshade}
\usepackage{tikz}
\usepackage{nameref}
\usepackage{zref-xr,zref-user}
\renewcommand*{\bibfont}{\tiny}

@@

\mode<presentation>{ 
  \usetheme{CambridgeUS}
  % http://identitystandards.illinois.edu/graphicstandardsmanual/generalguidelines/colors.html
  \definecolor{ilboldblue}{HTML}{002058}
  \definecolor{ilboldorange}{HTML}{E87722}
  \definecolor{ilblue}{HTML}{606EB2}
  \definecolor{ilorange}{HTML}{D45D00}
  \setbeamercolor{alerted text}{fg=ilboldorange}
  \setbeamercolor*{palette primary}{fg=ilblue,bg=ilorange}
  \setbeamercolor*{palette secondary}{fg=ilblue!20!white,bg=ilorange}
  \setbeamercolor*{palette tertiary}{bg=ilblue,fg=ilorange}
  \setbeamercolor*{palette quaternary}{fg=ilblue,bg=ilorange}

  \setbeamercolor*{sidebar}{fg=ilorange,bg=ilboldblue}

  \setbeamercolor*{palette sidebar primary}{fg=ilblue!10!white,bg=ilorange}
  \setbeamercolor*{palette sidebar secondary}{fg=ilorange}
  \setbeamercolor*{palette sidebar tertiary}{fg=ilblue}
  \setbeamercolor*{palette sidebar quaternary}{fg=ilorange}

  % \setbeamercolor*{titlelike}{parent=palette primary}
  \setbeamercolor{titlelike}{parent=palette primary,fg=ilboldblue,bg=ilorange}
  \setbeamercolor{frametitle}{fg=ilboldorange,bg=ilblue!80!white}
  \setbeamercolor{frametitle right}{fg=ilboldblue,bg=ilorange}

  \setbeamercolor*{separation line}{}
  \setbeamercolor*{fine separation line}{}
  \setbeamercovered{transparent}  
  \logo{\begin{tikzpicture}% Pale figure
      {\node[opacity=0.8]{\IfFileExists{figures/igb_wordmark.pdf}{\includegraphics[width=2cm,height=1cm,keepaspectratio]{figures/igb_wordmark}}{}%
        };}%
    \end{tikzpicture}}
}

\title[EVs of Placenta and Uterus]{Identifying Extracellular Vesicles of Placenta and Uterine 
  Origin Using RNA Expression Signatures}
\author[Don Armstrong et. al.]{Don L. Armstrong, Monica Uddin, Derek Wildman}
\institute[IGB]{Institute for Genomic Biology, Computing Genomes 
  for Reproductive Health, University of Illinois, Urbana-Champaign}
\subject{RNA expression}

\begin{document}

<<load.libraries,echo=FALSE,results="hide",warning=FALSE,message=FALSE,error=FALSE,cache=FALSE>>=
opts_chunk$set(dev="cairo_pdf",out.width="\\textwidth",out.height="0.8\\textheight",out.extra="keepaspectratio")
#opts_chunk$set(cache=TRUE, autodep=TRUE)
options(device = function(file, width = 8, height = 7, ...) {
  cairo_pdf(tempfile(), width = width, height = height, ...)
})
options(digits=2)
library("data.table")
library("ggplot2")
library("reshape2")
library("proto")
library("grid")
library("xtable")
library("caret")
library("pROC")

@@

      \begin{equation}
        \tau_g = \frac{\sum_{i=1}^{i=N} \left(1-\frac{X_{i,g}}{\mathrm{max}(X_g)}\right)}{N-1}
      \end{equation}
      \label{eq:tissue_specificity_index}
 \item $N$ is the number of tissues, $X_{i,g}$ is the mean expression
   of gene $g$ in tissue $i$ and $\mathrm{max}(X_g)$ is the maximal
   expression of gene $g$
    \end{itemize}
  \end{enumerate}

@@

\section{Methods}
\begin{frame}{Methods}
  \begin{itemize}
  % 
  \item \Sexpr{star.logs[grepl("Number of input reads",field),sum(as.numeric(value))]} %
    %
    RNAseq reads (\Sexpr{star.logs[grepl("Number of input reads",field),sum(as.numeric(value))]/length(star.logs[grepl("Number of input reads",field),value])} average per sample)%
    % 
  \item  \Sexpr{length(star.logs[grepl("Number of input reads",field),value])} %
    % 
    samples (supplemented with FPKMs from
    \Sexpr{nrow(predictions.caret.svm[["uterus"]][["training"]])+
      nrow(predictions.caret.svm[["uterus"]][["testing"]]) -
      length(star.logs[grepl("Number of input reads",field),value])} %
    %
    additional samples without raw data in the \ac{SRA})
    %

@@

\begin{frame}{Genes Characteristic of Uterus}
\begin{columns}
\column{0.6\textwidth}

<<uterus.specific.markers.figure,fig.width=8,fig.height=8,echo=FALSE>>=
print(specific.markers.plot("uterus")
      + xlab("Genes Characteristic of Uterus ")
      + ylab("Tissue"))
@
\column{0.4\textwidth}

\captionof{figure}{Expression of genes characteristic of uterus
  ($\tau_g \ge 0.98$) in uterus and all tissues with the second
  highest expression for any of the uterus-characterizing genes
  ordered by their tissue specificity. The known uterus-characterizing
  gene PAEP and short RNAs ZNFX1-AS1\_3 (87bp) and AL356310.1 (94bp)
  are highly characteristic of uterus.}
\end{columns}
\end{frame}

@@

\column{0.4\textwidth}
\captionof{figure}{Expression of genes characteristic of placenta
  ($\tau_g \ge 0.98$) with high expression ($\mathrm{FPKM} \ge 1024$)
  in placenta and all tissues with the second highest expression for
  any placenta-characterizing gene ordered by their specificity to
  placenta. The previously known placenta-characterizing PSG genes and
  CSH genes are nearly unique to placenta and the short RNAs mir-126,
  mir-622, and PAPPA-AS1 are less so.}
\end{columns}
\end{frame}

@@

\begin{frame}{Generating SVM}
 \begin{itemize}
 \item \ac{SVM} was generated using caret
    \cite{Kuhn2008:Buildingpredictivemodelsinr} and svmRadial
    \cite{Karatzoglou2004:kernlab}
  \item 10 cycles of 10 repeats and a
    tune length of 8

  \item training set representing $\approx 75\%$ of the samples
    ($\approx 2450$ samples total, including $\approx 35$ uterine or
    $\approx 60$ placenta) in each of the groups chosen at random,
  \item remaining samples making up a testing set ($\approx 820$
    samples)
  \end{itemize}
\end{frame}

\begin{frame}{Placenta and Uterus SVM}
  \centering
<<placenta.roc.curve,fig.width=8,fig.height=4,out.height="0.6\\textheight",echo=FALSE>>=
layout(matrix(1:2,1,2))
pl.roc.obj1 <- 
    plot.roc(as.numeric(predictions.caret.svm[["placenta"]][["testing"]][,"actual"])-1,
             as.numeric(predictions.caret.svm[["placenta"]][["testing"]][,"placenta"]),
             percent=TRUE,
             ## main="Training vs Testing set for Uterus",
             col="#002058"
             )
pl.roc.obj2 <- 
    lines.roc(as.numeric(predictions.caret.svm[["placenta"]][["training"]][,"actual"])-1,
              as.numeric(predictions.caret.svm[["placenta"]][["training"]][,"placenta"]),
              percent=TRUE,
              col="#E87722")
# testobj <- roc.test(rocobj1, rocobj2)
# text(50, 50, labels=paste("p-value =", format.pval(testobj$p.value)), adj=c(0, .5))

legend("bottomright",
       legend=c("Placenta Testing Set", "Placenta Training Set"),
       col=c("#002058", "#E87722"),
       lwd=2)

@@

legend("bottomright",
       legend=c("Uterus Testing Set", "Uterus Training Set"),
       col=c("#002058", "#E87722"),
       lwd=2)
@ 
\captionof{figure}{\ac{ROC} curve of the placenta \ac{SVM} (left) and
  uterus \ac{SVM} right) . Both \ac{SVM} are highly effective at
  distinguishing between samples of uterus origin and non-uterus
  origin.}
\label{fig:plac_ut_full_roc}
\end{frame}

@@

\begin{frame}{Reducing Reads}
  \begin{itemize}
  \item Reads sub-sampled from each sample 
  \item Weighted by the FPKM measured
  \item Run using the same trained SVM shown previously
  \end{itemize}
\end{frame}

@@

  The code and underlying data for this talk can be found at
  \begin{center}
    \qrcode[padding]{http://dla2.us/p/em2015}
    \url{http://dla2.us/p/em2015}
  \end{center}
\end{frame}

>>>>

\documentclass[ignorenonframetext]{beamer}
\usepackage{fontspec}
\setmainfont{FreeSerif}
\setsansfont{FreeSans}
\setmonofont{FreeMono}
\usepackage{url}
\usepackage{fancyhdr}
\usepackage{graphicx}
\usepackage[bf]{caption}
\usepackage{rotating}
\usepackage{wrapfig}
\usepackage{fancybox}
\usepackage{booktabs}
% \usepackage{multirow}
\usepackage{acronym}
\usepackage{qrcode}
\usepackage[absolute,overlay]{textpos}
\usepackage[backend=biber,natbib=true,hyperref=true,style=nature]{biblatex}
\addbibresource{references.bib}
% \usepackage[nomargin,inline,draft]{fixme}
% \newcommand{\DLA}[1]{\textcolor{red}{\fxnote{DLA: #1}}}
% \usepackage[hyperfigures,bookmarks,colorlinks,citecolor=black,filecolor=black,linkcolor=black,urlcolor=black]{hyperref}
\usepackage{texshade}
\usepackage{tikz}
\usetikzlibrary{positioning}
\usetikzlibrary{arrows.meta}
\usepackage{nameref}
\usepackage{zref-xr,zref-user}
\renewcommand*{\bibfont}{\tiny}
\usepackage{mathtools,cancel}

\renewcommand{\CancelColor}{\color{red}} %change cancel color to red

\makeatletter
\let\my@cancelto\cancelto %copy over the original cancelto command
\newcommand<>{\cancelto}[2]{\alt#3{\my@cancelto{#1}{#2}}{\mathrlap{#2}\phantom{\my@cancelto{#1}{#2}}}}
% redefine the cancelto command, using \phantom to assure that the
% result doesn't wiggle up and down with and without the arrow
\makeatother

@@

\mode<presentation>{ 
  \usetheme{CambridgeUS}
  \usecolortheme{crane}
%   % http://identitystandards.illinois.edu/graphicstandardsmanual/generalguidelines/colors.html
  \definecolor{ilboldblue}{HTML}{002058}
  \definecolor{ilboldorange}{HTML}{E87722}
  \definecolor{ilblue}{HTML}{606EB2}
  \definecolor{ilorange}{HTML}{D45D00}
%   \setbeamercolor{alerted text}{fg=ilboldorange}
%   \setbeamercolor*{palette primary}{fg=ilboldblue,bg=ilorange!70!white}
%   \setbeamercolor*{palette secondary}{fg=ilboldblue,bg=ilorange!60!white}
%   \setbeamercolor*{palette tertiary}{bg=ilblue!60!white,fg=ilboldorange}
%   \setbeamercolor*{palette quaternary}{fg=ilboldblue,bg=ilorange!80!white}
%   
%   \setbeamercolor*{sidebar}{fg=ilorange,bg=ilboldblue}
%   
%   \setbeamercolor*{palette sidebar primary}{fg=ilblue!10!white,bg=ilorange}
%   \setbeamercolor*{palette sidebar secondary}{fg=ilorange}
%   \setbeamercolor*{palette sidebar tertiary}{fg=ilblue}
%   \setbeamercolor*{palette sidebar quaternary}{fg=ilorange}
%   
%   % \setbeamercolor*{titlelike}{parent=palette primary}
%   \setbeamercolor{titlelike}{parent=palette primary,fg=ilboldblue,bg=ilorange}
%   \setbeamercolor{frametitle}{fg=ilboldorange,bg=ilblue!20!white}
%   \setbeamercolor{frametitle right}{fg=ilboldblue,bg=ilorange}
%   
%   \setbeamercolor*{separation line}{}
%   \setbeamercolor*{fine separation line}{}
%   \setbeamercovered{transparent}  
  \logo{\begin{tikzpicture}% Pale figure
      {\node[opacity=0.734]{\IfFileExists{figures/igb_wordmark.pdf}{\includegraphics[width=2cm,height=1cm,keepaspectratio]{figures/igb_wordmark}}{}%
        };}%
    \end{tikzpicture}}
}

\title[EVs of Placenta and Uterus]{Identifying Extracellular Vesicles of Placenta and Uterine 
  Origin Using RNA Expression Signatures}
\author[Don Armstrong et. al.]{Don L. Armstrong, Monica Uddin, Derek Wildman}
\institute[IGB]{Institute for Genomic Biology, Computing Genomes 
  for Reproductive Health, University of Illinois, Urbana-Champaign}
\subject{RNA expression}
\date{October 12, 2015}
\begin{document}

<<load.libraries,echo=FALSE,results="hide",warning=FALSE,message=FALSE,error=FALSE,cache=FALSE>>=
opts_chunk$set(dev="cairo_pdf",out.width="\\textwidth",out.height="0.8\\textheight",out.extra="keepaspectratio")
#opts_chunk$set(cache=TRUE, autodep=TRUE)
options(device = function(file, width = 8, height = 7, ...) {
  cairo_pdf(tempfile(), width = width, height = height, ...)
})
options(digits=2)
library("data.table")
library("ggplot2")
library("reshape2")
library("proto")
library("grid")
library("xtable")
library("caret")
library("pROC")
library("sampling")

@@

      \begin{equation}
        \tau_g = \frac{\sum_{i=1}^{i=N} \left(1-\frac{X_{i,g}}{\mathrm{max}(X_g)}\right)}{N-1}
      \end{equation}
      \label{eq:tissue_specificity_index}
 \item $N$ is the number of tissues, $X_{i,g}$ is the mean expression
   of gene $g$ in tissue $i$ and $\mathrm{max}(X_g)$ is the maximal
   expression of gene $g$
    \end{itemize}
\end{enumerate}
\only<2-4>{
\begin{textblock*}{64mm}(32mm,0.25\textheight)
\begin{block}{Tissue Specificity}
  \begin{itemize}
    \item Highly specific $\tau_g = \frac{\cancelto<3->{N-1}{\sum_{i=1}^{i=N} \left(1-\frac{X_{i,g}}{\mathrm{max}(X_g)}\right)}}{N-1} = 1$
    \item Not specific $\tau_g = \frac{\cancelto<4->{0}{\sum_{i=1}^{i=N} \left(1-\frac{X_{i,g}}{\mathrm{max}(X_g)}\right)}}{N-1} = 0$
    \end{itemize}
\end{block}
\end{textblock*}
}
\end{frame}

@@

\section{Methods}
\begin{frame}{Methods}
  \begin{center}
  \begin{tikzpicture}
    [rawreads/.style={rectangle,rounded corners=2mm,draw=ilblue!90!white,fill=ilblue!40!white,inner sep=2pt,minimum size=8mm,thick},
    processing/.style={rectangle,rounded corners=2mm,draw=ilblue!90!white,fill=ilboldblue!40!white,inner sep=2pt,minimum size=8mm,thick},
    arrow/.style={->,shorten >=1pt,>=stealth,thick},
    tissues/.style={rectangle,rounded corners=2mm,draw=ilorange!90!white,fill=ilorange!40!white,inner sep=2pt,minimum size=8mm,thick}]
    \node[tissues] (tissues) {\Sexpr{length(unique(na.omit(tissue.specific.genes[,tissue])))} tissues};
    \node[processing] (star) [above left=of tissues] {STAR+Cufflinks};
    \node[processing] (fpkm) [above right=of tissues] {FPKMs published};
    \node[rawreads] (samples) [above=of star] {\Sexpr{length(star.logs[grepl("Number of input reads",field),value])} samples in SRA};
    \node[rawreads] (samples noraw) [above=of fpkm] {\Sexpr{nrow(predictions.caret.svm[["uterus"]][["training"]])+
        nrow(predictions.caret.svm[["uterus"]][["testing"]]) -
        length(star.logs[grepl("Number of input reads",field),value])} samples not in SRA};
    \node[processing] (matrix) [below=of tissues] {FPKMs of 63967 genes $\times$ \Sexpr{nrow(predictions.caret.svm[["uterus"]][["training"]])+
        nrow(predictions.caret.svm[["uterus"]][["testing"]])} samples};
    \draw[arrow] (samples)--(star);
    \draw[arrow] (star)--(tissues);
    \draw[arrow] (samples noraw)--(fpkm);
    \draw[arrow] (fpkm)--(tissues);
    \draw[arrow] (tissues)--(matrix);
  \end{tikzpicture}
\end{center}
\end{frame}

\begin{frame}<beamer:0>{Methods}
  \begin{itemize}
  % 
  \item \Sexpr{star.logs[grepl("Number of input reads",field),sum(as.numeric(value))]} %
    %
    RNAseq reads (\Sexpr{star.logs[grepl("Number of input reads",field),sum(as.numeric(value))]/length(star.logs[grepl("Number of input reads",field),value])} average per sample)%
    % 
  \item  \Sexpr{length(star.logs[grepl("Number of input reads",field),value])} %
    % 
    samples (supplemented with FPKMs from
    \Sexpr{nrow(predictions.caret.svm[["uterus"]][["training"]])+
      nrow(predictions.caret.svm[["uterus"]][["testing"]]) -
      length(star.logs[grepl("Number of input reads",field),value])} %
    %
    additional samples without raw data in the \ac{SRA})
    %

@@

\begin{frame}{Genes Characteristic of Uterus}
\begin{columns}
\column{0.7\textwidth}

<<uterus.specific.markers.figure,fig.width=8,fig.height=8,echo=FALSE>>=
print(specific.markers.plot("uterus")
      + xlab("Genes Characteristic of Uterus ")
      + ylab("Tissue"))
@
\column{0.3\textwidth}

\captionof{figure}{Expression of genes characteristic of uterus
  ($\tau_g \ge 0.98$) in uterus and tissues with second-highest
  expression. The known uterus-characterizing gene
  progestagen-associated endometrial protein (PAEP) and short RNAs
  ZNFX1-AS1\_3 (87bp) and AL356310.1 (94bp) are highly characteristic
  of uterus.}
\end{columns}
\end{frame}

@@

\column{0.4\textwidth}
\captionof{figure}{Expression of genes characteristic of placenta
  ($\tau_g \ge 0.98$) with high expression ($\mathrm{FPKM} \ge 1024$)
  in placenta and tissues with the second highest expression. The
  previously known placenta-characterizing PSG genes and CSH genes are
  nearly unique to placenta and the short RNAs mir-126, mir-622, and
  PAPPA-AS1 are less so.}
\end{columns}
\end{frame}

@@

\subsection{SVM Methodology}

\begin{frame}{Generating SVM}
 \begin{itemize}
 \item \ac{SVM} is a machine learning technique which finds the
   hyperplane with the maximal margins which separates two groups
 \item \ac{SVM} was generated using caret
    \cite{Kuhn2008:Buildingpredictivemodelsinr} and svmRadial
    \cite{Karatzoglou2004:kernlab}
  \item 10 cycles of 10 repeats and a
    tune length of 8
  \end{itemize}
\end{frame}

\begin{frame}{Testing and Training Sets}
  \begin{center}
  \begin{tikzpicture}
    [training/.style={rectangle,rounded corners=2mm,draw=ilblue!90!white,fill=ilblue!40!white,inner sep=2pt,minimum size=8mm,thick},
    testing/.style={rectangle,rounded corners=2mm,draw=ilblue!90!white,fill=ilboldblue!40!white,inner sep=2pt,minimum size=8mm,thick},
    arrow/.style={->,shorten >=1pt,>=stealth,thick},
    sample/.style={rectangle,rounded corners=2mm,draw=ilorange!90!white,fill=ilorange!40!white,inner sep=2pt,minimum size=8mm,thick}]
    \node[sample] (samples) {\Sexpr{nrow(predictions.caret.svm[["uterus"]][["training"]])+
        nrow(predictions.caret.svm[["uterus"]][["testing"]])} samples};
\onslide<2->{    \node[training] (training) [below left=of samples] {\Sexpr{nrow(predictions.caret.svm[["uterus"]][["training"]])} training samples};
    \node[training] (training uterus) [below=of training] {\Sexpr{sum(predictions.caret.svm[["uterus"]][["training"]][,"actual"]=="uterus")} uterus,
      \Sexpr{sum(predictions.caret.svm[["placenta"]][["training"]][,"actual"]=="placenta")} placenta};

    \draw[arrow] (samples) -- node[above left=8pt]{75\%} (training);
    \draw[arrow] (training) -- (training uterus);
    }
\onslide<3->{    \node[testing] (testing) [below right=of samples] {\Sexpr{nrow(predictions.caret.svm[["uterus"]][["testing"]])} testing samples};
    \node[testing] (testing uterus) [below=of testing] {\Sexpr{sum(predictions.caret.svm[["uterus"]][["testing"]][,"actual"]=="uterus")} uterus,
      \Sexpr{sum(predictions.caret.svm[["placenta"]][["testing"]][,"actual"]=="placenta")} placenta};
    \draw[arrow] (samples) -- node[above right=8pt]{25\%} (testing);
    \draw[arrow] (testing) -- (testing uterus);}
  \end{tikzpicture}
\end{center}
\end{frame}

\begin{frame}{Placenta SVM: Training and Testing}
  \begin{columns}
    \column{0.6\textwidth}
<<placenta.roc.curve,fig.width=4,fig.height=4,out.height="0.7\\textheight",echo=FALSE>>=
# layout(matrix(1:2,1,2))
par(mar=c(0,0,0,0))
pl.roc.obj1 <- 
    plot.roc(as.numeric(predictions.caret.svm[["placenta"]][["testing"]][,"actual"])-1,
             as.numeric(predictions.caret.svm[["placenta"]][["testing"]][,"placenta"]),
             percent=TRUE,
             ## main="Training vs Testing set for Uterus",
             col="#002058"
             )
pl.roc.obj2 <- 
    lines.roc(as.numeric(predictions.caret.svm[["placenta"]][["training"]][,"actual"])-1,
              as.numeric(predictions.caret.svm[["placenta"]][["training"]][,"placenta"]),
              percent=TRUE,
              col="#E87722")
# testobj <- roc.test(rocobj1, rocobj2)
# text(50, 50, labels=paste("p-value =", format.pval(testobj$p.value)), adj=c(0, .5))

legend("bottomright",
       legend=c("Placenta Testing Set", "Placenta Training Set"),
       col=c("#002058", "#E87722"),
       lwd=2)
@ 
\column{0.4\textwidth}
\captionof{figure}{\ac{ROC} curve of the placenta \ac{SVM}. The
  \ac{SVM} is highly effective at distinguishing between samples of
  placental origin and non-placental origin.}
\label{fig:plac_full_roc}
\end{columns}
\end{frame}

\begin{frame}{Uterus SVM: Training and Testing Sets}
  \begin{columns}
    \column{0.6\textwidth}
<<uterus.roc.curve,fig.width=4,fig.height=4,out.height="0.7\\textheight",echo=FALSE>>=

@@

legend("bottomright",
       legend=c("Uterus Testing Set", "Uterus Training Set"),
       col=c("#002058", "#E87722"),
       lwd=2)
@ 
\column{0.4\textwidth}
\captionof{figure}{\ac{ROC} curve of the uterus \ac{SVM}. The \ac{SVM}
  is highly effective at distinguishing between samples of uterus
  origin and non-uterus origin.}
\label{fig:ut_full_roc}
\end{columns}
\end{frame}

@@

\begin{frame}{Reducing Reads}
  \begin{itemize}
  \item Reads sub-sampled from each sample 
  \item Weighted by the FPKM measured
  \item Run using the same trained SVM shown previously
  \end{itemize}
  \only<2->{
\begin{textblock*}{100mm}(20mm,0.25\textheight)
\begin{block}{Sub sampling}
<<calc.reduced,echo=FALSE,results="asis">>=
reduced.reads <- function(fpkms,num.reads) {
    non.zero <- fpkms > 0
    ret.val <- rep.int(0,length(fpkms))
    if (!any(non.zero)) {
        return(fpkms)
    }
    inc.prob <- inclusionprobabilities(fpkms[non.zero],1)
    ret.val[non.zero] <-
        apply(sapply(1:(num.reads/1),function(y){UPrandomsystematic(inc.prob,0)}),1,sum)
    names(ret.val) <- names(fpkms)
    ret.val
}
set.seed(1021)
reads <- c("A"=1000,
           "B"=2000,
           "C"=20,
           "D"=5000)
reads.to.table <- function(read,reads){
    data.table("Total Reads"=read,
               "Gene A"=reads["A"],
               "Gene B"=reads["B"],
               "Gene C"=reads["C"],
               "Gene D"=reads["D"])
}
rr.table <- list(reads.to.table("Orig. FPKM",reads))
i <- 0
for (read in c(500,500,100,100,5,5,5)){
    i <- i+1
    reads <- reduced.reads(reads,read)
    rr.table[[paste0("read.",read,'.',i)]] <- 
        reads.to.table(read,reads)
}
print(xtable(rbindlist(rr.table),
             digits=0
             ),
      include.rownames=FALSE)
@

\end{block}
\end{textblock*}
}

@@

  The code and underlying data for this talk can be found at
  \begin{center}
    \qrcode[padding]{http://dla2.us/p/em2015}
    \url{http://dla2.us/p/em2015}
  \end{center}
  \begin{itemize}
  \item University of Illinois and Institute for Genomic Biology
    Startup Funds to Derek and Monica
  \end{itemize}
\end{frame}
